
# R project for converting bookmaker odds to probabilities to Poisson goalscoring means

Functions are in the file `functions.R`.

## packages

```{r}
library(tidyverse)
library(rvest)
source("functions.R")
```

Make a dataframe of competitions to get. These are samples; you can add others. (I wrote this during the delayed Euro 2020.) The column `short` appears in the output, rather than the long URL.

```{r}
leagues <- tribble(
  ~sheet_url, ~short,
#  "https://www.oddschecker.com/football/english/fa-cup", "enf", 
  # "https://www.oddschecker.com/football/champions-league", "euc", 
  # "https://www.oddschecker.com/football/europa-league", "eue", 
  "https://www.oddschecker.com/football/euro-2020", "ec", 
)
leagues
```

run for all leagues

```{r, warning=FALSE}
make_lambdas(leagues) %>% knitr::kable()
```

The bookies' probability of a draw is near 30% for evenly-matched teams, which seems too high. Maybe also the Poisson means are too low. Using a discount like 0.9 makes the draw probability lower and also makes the means higher (it makes the draw probability 90% of what it was, and rescales the other probabilities in proportion):

```{r, warning=FALSE}
make_lambdas(leagues, discount = 0.9) %>% knitr::kable()
```

The means are now a bit higher.